The role of emotional factors in face processing abilities in Autism Spectrum Conditions

### 2023-07-09 manuscript.Rmd
Finished analysis and added autobuild

packagelist <- c('pwr','rstatix','kableExtra','MASS','lm.beta')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

@@

In regression series 1, we enetered age, gender, and ethnicity entered as predictors in step 1 to control for these broad demographic effects on performance. In step 2, we enetered our alexithymia measure (the TAS-20), and then step three included our anxiety and depressions measures (the HADS), and step 4 included our autism trait measure (the AQ-28). All self-report measures were entered as continuous variables.

@@

We will planned to include some simple correlational analyses, descriptive statistics, and t-tests to further clarify any group differences, and directions of effect. We also examined the group differences of participants who meet the commonly used threshold for alexithymia (a score of 61 of above on the TAS-20), and those who do not, as previous research indicates we will also find a difference between these groups [@cook2013a]. This was done via a series of non-parametric tests, to explore whether those who are above the threshold are associated with higher levels of depression, anxiety, autistic traits, and poor facial emotion and identity recognition.

@@

In our first series of regressions, a continuous measure of autistic traits, the AQ28, was entered in the final step. Table \@ref(tab:table3) summarises the results of this regression series. For emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1s and 2 (although the addition of the TAS in step 2 did not lead to a significant increase in the variance explained). The only significant predictor was gender, specifically the dummy variable indicating “other” gender. See sub-section “The role of gender” for follow up tests on gender effects on emotion PSE. Table 4 summarises the coefficients for the regressions with significant models.

@@

Table 5 summarises the results of the regression series that considered the role of autistic status. For emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1, 2 and 4, although beyond model 1 no additional steps added significant explained variance. Table 6 summarises the coefficients for the regressions with significant models.

Table 7 summarises the results of the regression series that considered the role of self-identification. Similar to the regression series reported above, emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1, 2 and 4, although beyond model 1 no additional steps added significant explained variance. Table 8 summarises the coefficients for the regressions with significant models.

>>>>

packagelist <- c('pwr','rstatix','kableExtra','lm.beta','coin')
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

```{r regseries2}

# stepwise regression series 2

# Emotion Attribution DV
#define model with all predictors
all <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_EA2 <- data[i,]

# intercept only (null) model
EAmodel0b <- lm(EMOATTINV ~ 1, data=data_EA2)

# first stepwise entry
EAmodel1b <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_EA2)

# second stepwise entry
EAmodel2b <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_EA2)

# third stepwise entry
EAmodel3b <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_EA2)

# fourth stepwise entry
EAmodel4b <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data_EA2)

# Identity Attribution DV
#define model with all predictors
all <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_IA2 <- data[i,]

# intercept only (null) model
IAmodel0b <- lm(IDATTINV ~ 1, data=data_IA2)

# first stepwise entry
IAmodel1b <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_IA2)

# second stepwise entry
IAmodel2b <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_IA2)

# third stepwise entry
IAmodel3b <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_IA2)

# fourth stepwise entry
IAmodel4b <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data_IA2)

# Emotion PSE DV
#define model with all predictors
all <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_EP2 <- data[i,]

# intercept only (null) model
EPmodel0b <- lm(EMOPSE ~ 1, data=data_EP2)

# first stepwise entry
EPmodel1b <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_EP2)

# second stepwise entry
EPmodel2b <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_EP2)

# third stepwise entry
EPmodel3b <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_EP2)

# fourth stepwise entry
EPmodel4b <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data_EP2)

# Identity PSE DV
#define model with all predictors
all <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_IP2 <- data[i,]

# intercept only (null) model
IPmodel0b <- lm(IDPSE ~ 1, data=data_IP2)

# first stepwise entry
IPmodel1b <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_IP2)

# second stepwise entry
IPmodel2b <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_IP2)

# third stepwise entry
IPmodel3b <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_IP2)

# fourth stepwise entry
IPmodel4b <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Group_NTorASC, data=data_IP2)

```{r regseries3}

# stepwise regression series 3

# Emotion Attribution DV
#define model with all predictors
all <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_EA3 <- data[i,]

# intercept only (null) model
EAmodel0c <- lm(EMOATTINV ~ 1, data=data_EA3)

# first stepwise entry
EAmodel1c <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_EA3)

# second stepwise entry
EAmodel2c <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_EA3)

# third stepwise entry
EAmodel3c <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_EA3)

# fourth stepwise entry
EAmodel4c <- lm(EMOATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data_EA3)

# Identity Attribution DV
#define model with all predictors
all <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_IA3 <- data[i,]

# intercept only (null) model
IAmodel0c <- lm(IDATTINV ~ 1, data=data_IA3)

# first stepwise entry
IAmodel1c <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_IA3)

# second stepwise entry
IAmodel2c <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_IA3)

# third stepwise entry
IAmodel3c <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_IA3)

# fourth stepwise entry
IAmodel4c <- lm(IDATTINV ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data_IA3)

# Emotion PSE DV
#define model with all predictors
all <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_EP3 <- data[i,]

# intercept only (null) model
EPmodel0c <- lm(EMOPSE ~ 1, data=data_EP3)

# first stepwise entry
EPmodel1c <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_EP3)

# second stepwise entry
EPmodel2c <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_EP3)

# third stepwise entry
EPmodel3c <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_EP3)

# fourth stepwise entry
EPmodel4c <- lm(EMOPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data_EP3)

# Identity PSE DV
#define model with all predictors
all <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data)

# exclude outliers using cook's distance threshold
CD <- cooks.distance(all)
i <- which(CD<cookthresh)
data_IP3 <- data[i,]

# intercept only (null) model
IPmodel0c <- lm(IDPSE ~ 1, data=data_IP3)

# first stepwise entry
IPmodel1c <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black, data=data_IP3)

# second stepwise entry
IPmodel2c <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL, data=data_IP3)

# third stepwise entry
IPmodel3c <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7, data=data_IP3)

# fourth stepwise entry
IPmodel4c <- lm(IDPSE ~ AGE + Dum_male + Dum_other + Dum_Asian + Dum_Mixed + Dum_Black + TASTOTAL + HANX7 + HDEP7 + Dum_FormalDiag + Dum_SelfDiag, data=data_IP3)

@@

In regression series 1, we entered age, gender, and ethnicity entered as predictors in step 1 to control for these broad demographic effects on performance. In step 2, we entered our alexithymia measure (the TAS-20), and then step three included our anxiety and depressions measures (the HADS), and step 4 included our autism trait measure (the AQ-28). All self-report measures were entered as continuous variables.

@@

We planned to include some simple correlational analyses, descriptive statistics, and t-tests to further clarify any group differences, and directions of effect. We also examined the group differences of participants who meet the commonly used threshold for alexithymia (a score of 61 of above on the TAS-20), and those who do not, as previous research indicates we will also find a difference between these groups [@cook2013a]. This was done via a series of non-parametric tests, to explore whether those who are above the threshold are associated with higher levels of depression, anxiety, autistic traits, and poor facial emotion and identity recognition.

@@

In our first series of regressions, a continuous measure of autistic traits, the AQ28, was entered in the final step. Table \@ref(tab:table3) summarises the results of this regression series. For emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1s and 2 (although the addition of the TAS in step 2 did not lead to a significant increase in the variance explained). The only significant predictor was gender, specifically the dummy variable indicating “other” gender. See sub-section “The role of gender” for follow up tests on gender effects on emotion PSE. Table \@ref(tab:table4) summarises the coefficients for the regressions with significant models.

@@

Table \@ref(tab:table5) summarises the results of the regression series that considered the role of autistic status. For emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1, 2 and 4, although beyond model 1 no additional steps added significant explained variance. Table \@ref(tab:table6) summarises the coefficients for the regressions with significant models.

``` {r table5}

table5data <- data.frame(matrix(0,nrow=6,ncol=9))

table5data[1,] <- c('','','F change,','','F change,','','F change,','','F change,')
table5data[2,] <- c('','F (Df), p-value','p-value','F (Df), p-value','p-value','F (Df), p-value','p-value','F (Df), p-value','p-value')
table5data[,1] <- c('','','Model 1','Model 2','Model 3','Model 4')

a <- summary(EAmodel1b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[3,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel2b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[4,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel3b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[5,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel4b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[6,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel1b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[3,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel2b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[4,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel3b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[5,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel4b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[6,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel1b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table5data[3,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel2b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table5data[4,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel3b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table5data[5,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel4b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table5data[6,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel1b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[3,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel2b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[4,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel3b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[5,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel4b)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table5data[6,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- anova(EAmodel0b,EAmodel1b)
table5data[3,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EAmodel1b,EAmodel2b)
table5data[4,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=2,accuracy=0.001,leading.zero=F))

a <- anova(EAmodel2b,EAmodel3b)
table5data[5,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EAmodel3b,EAmodel4b)
table5data[6,3] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel0b,IAmodel1b)
table5data[3,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel1b,IAmodel2b)
table5data[4,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel2b,IAmodel3b)
table5data[5,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IAmodel3b,IAmodel4b)
table5data[6,5] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel0b,EPmodel1b)
table5data[3,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=2,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel1b,EPmodel2b)
table5data[4,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel2b,EPmodel3b)
table5data[5,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(EPmodel3b,EPmodel4b)
table5data[6,7] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IPmodel0b,IPmodel1b)
table5data[3,9] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IPmodel1b,IPmodel2b)
table5data[4,9] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=2,accuracy=0.001,leading.zero=F))

a <- anova(IPmodel2b,IPmodel3b)
table5data[5,9] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

a <- anova(IPmodel3b,IPmodel4b)
table5data[6,9] <- paste0(round(a[2,5],digits=2),', ',p_format(a[2,6],digits=3,accuracy=0.001,leading.zero=F))

knitr::kable(table5data, booktabs = T, col.names = NULL, caption='Regression Series 2 (Autistic vs Non-autistic Group status entered in Step 4).', align='lllllllll') %>%
  row_spec(2, hline_after=T) %>%
 kableExtra::add_header_above(c('','Total N (ASC,TD) = 174 (77, 97)'=2,'Total N (ASC,TD) = 170 (75, 95)'=2,'Total N (ASC,TD) = 174 (77, 97)'=2,'Total N (ASC,TD) = 176 (78, 98)'=2),bold=F,align='l') %>%
  kableExtra::add_header_above(c('','Emotion Attribution'=2,'Identity Attribution'=2,'Emotion PSE'=2,'Identity PSE'=2),bold=F,align='l',line=F) %>% 
  kable_styling(latex_options='HOLD_position',font_size=5)

``` {r table6}

table6data <- data.frame(matrix(0,nrow=32,ncol=5))

colnames(table6data) <- c('Model','','Beta','t','p-value')
table6data[,1] <- ''
table6data[c(1,7,14,23),3] <- ''
table6data[c(1,7,14,23),1] <- 1:4
table6data[,2] <- c('(Constant)','Age','Male gender','Other gender','Asian ethnicity','Mixed ethnicity','(Constant)','Age','Male gender','Other gender','Asian ethnicity','Mixed ethnicity','TAS-TOTAL','(Constant)','Age','Male gender','Other gender','Asian ethnicity','Mixed ethnicity','TAS-TOTAL','HADS Anxiety','HADS Depression','(Constant)','Age','Male gender','Other gender','Asian ethnicity','Mixed ethnicity','TAS-TOTAL','HADS Anxiety','HADS Depression','Autism Group (autistic or non-autistic)')

betas <- lm.beta(EPmodel1b)
table6data[2:6,3] <- round(betas$standardized.coefficients[2:6],digits=3)

betas <- lm.beta(EPmodel2b)
table6data[8:13,3] <- round(betas$standardized.coefficients[c(2:6,8)],digits=3)

betas <- lm.beta(EPmodel3b)
table6data[15:22,3] <- round(betas$standardized.coefficients[c(2:6,8:10)],digits=3)

betas <- lm.beta(EPmodel4b)
table6data[24:32,3] <- round(betas$standardized.coefficients[c(2:6,8:11)],digits=3)

vals <- summary(EPmodel1b)$coefficients
table6data[1:6,4] <- round(vals[,3],digits=3)
table6data[1:6,5] <- p_format(vals[,4], digits=1, accuracy = 0.001, leading.zero=FALSE)

vals <- summary(EPmodel2b)$coefficients
table6data[7:13,4] <- round(vals[,3],digits=3)
table6data[7:13,5] <- p_format(vals[,4], digits=1, accuracy = 0.001, leading.zero=FALSE)

vals <- summary(EPmodel3b)$coefficients
table6data[14:22,4] <- round(vals[,3],digits=3)
table6data[14:22,5] <- p_format(vals[,4], digits=1, accuracy = 0.001, leading.zero=FALSE)

vals <- summary(EPmodel4b)$coefficients
table6data[23:32,4] <- round(vals[,3],digits=3)
table6data[23:32,5] <- p_format(vals[,4], digits=1, accuracy = 0.001, leading.zero=FALSE)

knitr::kable(table6data, booktabs = T,  caption='Coefficients for Emotion PSE Regression series 2.', align='llrrr') %>%
  kable_styling(latex_options='HOLD_position')

Table \@ref(tab:table7) summarises the results of the regression series that considered the role of self-identification. Similar to the regression series reported above, emotion attribution thresholds, identity attribution thresholds, and identity PSE, no model was significant at any step. For emotion PSE, the regression model was significant at steps 1, 2 and 4, although beyond model 1 no additional steps added significant explained variance. Table \@ref(tab:table8) summarises the coefficients for the regressions with significant models.

``` {r table7}

table7data <- data.frame(matrix(0,nrow=6,ncol=9))

table7data[1,] <- c('','','F change,','','F change,','','F change,','','F change,')
table7data[2,] <- c('','F (Df), p-value','p-value','F (Df), p-value','p-value','F (Df), p-value','p-value','F (Df), p-value','p-value')
table7data[,1] <- c('','','Model 1','Model 2','Model 3','Model 4')

a <- summary(EAmodel1c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[3,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel2c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[4,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel3c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[5,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EAmodel4c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[6,2] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel1c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[3,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel2c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[4,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel3c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[5,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IAmodel4c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[6,4] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel1c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table7data[3,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel2c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table7data[4,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel3c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table7data[5,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(EPmodel4c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=2, accuracy = 0.001, leading.zero=FALSE)
table7data[6,6] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel1c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[3,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel2c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[4,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)

a <- summary(IPmodel3c)
pval <- p_format(pf(a$fstatistic[1],a$fstatistic[2],a$fstatistic[3],lower.tail=FALSE), digits=3, accuracy = 0.001, leading.zero=FALSE)
table7data[5,8] <- paste0(round(a$fstatistic[1],digits=2), ' (',a$fstatistic[2],',',a$fstatistic[3],'), ',pval)
